Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks

### 2020-03-11 paper/paper.tex
write some paper

	\section{EXPERIMENT}\label{sec:experiment}
	In this section, we showed and analyzed the training result.
	We compared our model with six neural network based algorithms i.e.,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{sharma2016hyperspectral},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	the CapsNet that is identical to our DCCN model except the spectral channel and the machine learning algorithm SVM\@.
	The accuracy metrics we used includes overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).

@@

	\subsection{Experiment Setup}Usually, a HSI dataset has labeled and unlabeled pixels.
	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
	and the rest of the labeled pixels was used to validate the model.
	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}

@@

	\begin{figure}[htbp]
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=0.9\textwidth]{pic/p5/pc/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=0.9\textwidth]{pic/p5/pu/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=0.9\textwidth]{pic/p5/sl/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=0.9\textwidth]{pic/p5/sa/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
		\label{testMaps}
	\end{figure}

	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
	SVM,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{sharma2016hyperspectral},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	CapsNet and DCCN together in table~\ref{result}
	\begin{table}[htb]
		\tiny
		\centering
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			 &\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
			\hline
			\begin{tabular}{c}
				\textbf{model}\\
				\hline
				{SVM}\\
				{1D CNN\cite{hu2015deep}}\\
				{2D CNN\cite{sharma2016hyperspectral}}\\
				{3D CNN\cite{hamida20183}}\\
				{3D FCN\cite{lee2016contextual}}\\
				{CNN-MRF\cite{cao2018hyperspectral}}\\
				{CapsNet}\\
				{DCCN}\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}\\
			\hline
		\end{tabular}
		\caption{Final result of all adopted models.}
	\end{table}\label{result}

	\subsection{Convergence analysis}\label{subsec:convergence}
	In this subsection, we evaluated the convergence of our proposed network.
	Figure~\ref{accandloss}
	\begin{figure}[htb]
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/lossAndAcc.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/pu/1/img/lossAndAcc.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/sl/1/img/lossAndAcc.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/sa/1/img/lossAndAcc.eps}
			\caption{}
		\end{subfigure}
		\caption{Accuracy and loss of the proposed DCCN model with increasing iterations during the training process.
		The horizontal axis represents 100 training epochs.
		The corresponding relationship between the plot and dataset are:(a) for Pavia Center, (b) for Pavia University,
			(c) for Salinas Vallet and (d) for Salinas A}
	\end{figure}\label{accandloss}

	\section{DISCUSSION}\label{sec:discussion}

>>>>

	\section{EXPERIMENT}\label{sec:experiment}
	In this section, we showed and analyzed the training result.
	We compared our model with six neural network based algorithms i.e.,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{sharma2016hyperspectral},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	the CapsNet that is identical to our DCCN model except the spectral channel, and the machine learning algorithm
	SVM\@.
	The competing neural network based algorithms are trained using the best network structure and hyper-parameters
	proposed by the authors in their papers, and the SVM algorithm was trained using 10\% of the total labeled pixels
	as the DCCN model.
	The accuracy metrics we used include overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).

@@

	\subsection{Experiment Setup}Usually, a HSI dataset has labeled and unlabeled pixels.
	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
	and all pixels except those chosen for training were used to validate the model.
	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}

@@

	\begin{figure}[htbp]
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=0.9\textwidth]{pic/p5/pc/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=0.9\textwidth]{pic/p5/pu/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=0.9\textwidth]{pic/p5/sl/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=0.9\textwidth]{pic/p5/sa/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A.}
		\label{testMaps}
	\end{figure}

	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
	SVM,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{sharma2016hyperspectral},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	CapsNet and DCCN together in table~\ref{result}.
	From the results reported in table~\ref{result}, we can observe that our proposed DCCN model outperforms all the
	other seven state-of-art models on all 4 dataset.
	Among all competitors in this experiment, 3D CNN\cite{hamida20183} and the CapsNet model performed relatively second
	best, since both of the two model achieved second high accuracy on different dataset.
	This is expected because both of the two algorithm are spectral-spatial based so they can utilize more information,
	compared to the 2D CNN, FCN, SVM and CNN-MRF classifiers, to classify the HSI pixels.
	Nevertheless, our DCCN model can consistently outperform the second-best algorithm with an average \textbf{fill data
	here} for AA, OA, $\kappa$.

	\begin{table}[htb]
		\tiny
		\centering
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			 &\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
			\hline
			\begin{tabular}{c}
				\textbf{model}\\
				\hline
				{SVM}\\
				{1D CNN\cite{hu2015deep}}\\
				{2D CNN\cite{sharma2016hyperspectral}}\\
				{3D CNN\cite{hamida20183}}\\
				{3D FCN\cite{lee2016contextual}}\\
				{CNN-MRF\cite{cao2018hyperspectral}}\\
				{CapsNet}\\
				{DCCN}\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}\\
			\hline
		\end{tabular}
		\caption{Final result of all adopted models.}
		\label{result}
	\end{table}

	In figure~\ref{pupm,pcpm,svpm,sapm} we presented the classification maps outputted by our DCCN and seven competitor
	model after the training process.
	\begin{figure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\label{pcpm}
	\end{figure}
	\begin{figure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\label{pupm}
	\end{figure}
	\begin{figure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\label{svpm}
	\end{figure}
	\begin{figure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
			\caption{}
		\end{subfigure}
		\label{sapm}
	\end{figure}

	Finally, we presented the probability maps the eight algorithms produced of the four HSI dataset in
	figure~\ref{pcpd ,pupd,svpd,sapd}.
	\begin{figure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\label{pcpd}
	\end{figure}
	\begin{figure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\label{pupd}
	\end{figure}
	\begin{figure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\label{svpd}
	\end{figure}
	\begin{figure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
			\caption{}
		\end{subfigure}
		\label{sapd}
	\end{figure}

	\subsection{Convergence analysis}\label{subsec:convergence}
	In this subsection, we evaluated the convergence of our proposed network.
	Figure~\ref{accandloss} showed the training process of our DCCN model for 4 dataset separately.
	\begin{figure}[htb]
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/lossAndAcc.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/pu/1/img/lossAndAcc.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/sl/1/img/lossAndAcc.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{0.24\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/sa/1/img/lossAndAcc.eps}
			\caption{}
		\end{subfigure}
		\caption{Accuracy and loss of the proposed DCCN model with increasing iterations during the training process.
		The horizontal axis represents 100 training epochs.
		The corresponding relationship between the plot and dataset are:(a) for Pavia Center, (b) for Pavia University,
			(c) for Salinas Vallet and (d) for Salinas A.}
		\label{accandloss}
	\end{figure}

	\section{DISCUSSION}\label{sec:discussion}
	In this sector, we further explored the effect of different hyper-parameters to the DCCN\@.
	We used the Pavia University and Salinas A dataset to train and test our model, so that we can observe the model's
	performance on both large and small dataset.
	We first tested the effect of different size of training set with a fixed patch size of 7*7, and then tested the
	effect of
